\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2023-02-27 paper/main.tex
uncomment abstract and move other commented sections around

\begin{abstract}
% Repeated games are vastly use in evolutionary game theory to explain cooperation in a variety of environments. Although existing models have shaped
% our understanding of human cooperation, hey often work with idealized
% assumptions. In an evolutionary process, individuals imitate other individuals
% of the population based on their fitness. It is commonly assumed that an
% individual computes their fitness after interacting with a representative sample
% of the population, and remembering all the interactions they participated in. In
% real life, we do not always remember all our interactions, instead we rather
% recall our most recent ones.

% Here, we introduce a framework that allows individuals to estimate their fitness
% based on a minimum of social information. We explore the difference between our
% framework and the classical framework using computer simulations. We present
% results for the most commonly used classes of symmetric \(2 \times 2\) games.
% The simulations show that, in the prisoner's dilemma individuals with limited
% memory tend to adopt less generous strategies and they achieve less cooperation
% than in the classical scenario. In contrast, in the stag-hunt and the harmony
% game, the impact of memory is less striking. Here individuals with limited
% memory perform nearly as well as individuals with full memory. Finally, we
% observe that the snowdrift game is the only game for which cooperation can be
% underestimated in the classical scenario.
\end{abstract}

>>>>

\begin{abstract}
Repeated games are vastly use in evolutionary game theory to explain cooperation
in a variety of environments. Although existing models have shaped our
understanding of human cooperation, hey often work with idealized assumptions.
In an evolutionary process, individuals imitate other individuals of the
population based on their fitness. It is commonly assumed that an individual
computes their fitness after interacting with a representative sample of the
population, and remembering all the interactions they participated in. In real
life, we do not always remember all our interactions, instead we rather recall
our most recent ones.

Here, we introduce a framework that allows individuals to estimate their fitness
based on a minimum of social information. We explore the difference between our
framework and the classical framework using computer simulations. The
simulations show that, in the prisoner's dilemma individuals with limited memory
tend to adopt less generous strategies and they achieve less cooperation than in
the classical scenario.
\end{abstract}
